30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-12 paper.tex
Added an introduction to chapter IV and some text to chapter VI

\section{Problems when decentralizing}
		hier komt de introductie

@@

		\subsection{MorphMix}
			MorphMix functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

			MIX networks are high latency and traffic moves slow. Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order. Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead. MorphMix has been developed as a low latency and high performance network. As such, it will not hold messages for very long, nor will it use cover traffic.

			In contrast to Tor, MorphMix does not feature a centralized node discovery. Instead, every node is free to chose a set of next nodes that will be the continuation of the anonymous tunnel. A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel. To prevent this, a witness node is appointed to mediate the setup of the anonymous tunnel. Although this makes the possibility of such an attack more difficult, it is not impossible.

			An important part of MorphMix is the ability to detect malicious tunnels. Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly. Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel. This will reveal itself in the fact that the probability of the selection of certain nodes is increased. By using this information it becomes possible, to an extent, to detect malicious tunnels.

@@

		\subsection{Comparison and differences}
			Comparison table.

>>>>

\section{Problems when decentralizing}
		As we saw in the previous section, we would like to have a decentralized anonymous network. This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us. Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry. These networks will be described in more detail in the next chapter. Among these networks are some overlay anonymous networks such as Tarzan.

		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor. In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.

@@

@@

		In the last section, we discussedexisting decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:
\begin{itemize}
\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
\item Public implementation. For each network we will explain whether a public implementation is available.
\item Used in practice. Is the network used in practice?
\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
\end{itemize}
